\chapter{Sessions and Parties}
In the West Marches Campaign there are fairly specific rules in terms of parties and sessions. While some of these may seems obtuse they exist to ensure the smooth running of the West Marches Campaign and to ensure everyone has an fun time.
\section{Party Size}
A party must have a minimum of 3 players and a maximum of 6 players. There may be an exception to this rule however it is incredibly rare and only for special occasions. It should be noted that all dungeons and encounters is balanced around having parties containing 5 members.
\section{Party Members}
The only limitation in terms of party members is that a character cannot play with another character more than 2 sessions in a row.
This rule is in place to ensure that players to not form into consistent groups that do not interact with each other. \newline
It should be noted that this rule applies to characters and not players. If your character dies then your new character is assumed to not have played with any other characters and that no other characters have played with your new one.
\section{Session frequency}
A player may only participate in one session a week. There is no exception to this rule. A session may take place over 2 days if it over runs but no more.
\section{Booking a session}
Sessions must be booked by 18:00 on the Thursday before the week before you want the session. There is no exception to this rule. It is requested that you do so earlier though so that we have time to prepare for the session. You must ensure that the party and session conforms to all of the rules in this section. You must specify the location your party is going to, this can not be changed after submitting a request. \newline 
The party members can change after booking so long as the new membership conforms to all other rules in this chapter. You must also make your Dungeon Master aware of any changes to the party as early as possible. \newline
You can book a session using \href{ https://goo.gl/forms/rzNrDHNviYnMTSXA2}{this Google form} and a list of sessions that are happening can be found at \href{ https://docs.google.com/spreadsheets/d/1MQKPtY3KcZKCh2T7X1U4zbln39ESutp5Gm-XhqRATZ0/edit?usp=sharing}{this Google spreadsheet}
\section{Downtime Activities}
If you do not partake in any session in one week (Noting that a week starts on Monday and ends on Saturday for the purposes of this) then you may instead elect to do a downtime activity.
\newline
Examples of downtime activities you can do can be found in both the Dungeon Masters Guide and in the Unearthed Arcana Downtime document. Most, though not all, downtime time activities take one week and one week real time counts as 4 weeks in game time. In order to do a downtime activity you must message a Dungeon Master before the end of the week. 
\begin{paperbox}[float=!t]{Downtime activities}
  It should be noted that downtime activities do not constitute as sessions and therefore taking downtime will not reset the counters measuring consecutive sessions with the same character. 
\end{paperbox}