\chapter{Westfast}
Westfast is the small town set up by The West Marches Commission. It is located 120 miles north west of the western exit to the Hans Gate Pass. 
\section{People of Westfast}
West fast is populated by mainly adventures , merchants and others looking to find a new life is the West Marches. There are also a few major NPC's that inhabit Westfast.
\subsection{Helmend Mund, The West Marches Commissioner}
Short, even for a dwarf, and somewhat pudgy. Helmend’s hair and beard is pulled back in neat dreadlocks, with a set of wire-rimmed spectacles sitting on his nose. He’s frequently found doing paperwork, extorting others to do paperwork, and smoking his particular variety of dwarven pipe-weed. In all matters, he adheres to regulation absolutely, and expects as much from others. 
\newline
He wears the holy symbol of Tyrel around his neck, a numbered count that indicates his position in the church. Occasionally it will count down, and Helmend will nod approvingly. 
\newline
Attempting to get any clerical assistance from Helmend will result in him handing the requester reams of paperwork that must be filled to qualify for such.

\subsection{Magna Virum, The Town Crier}
Magna is an extremely loud and theatrical High Elf, well-suited to his position as town-crier. His entrance into a room is accompanied by loud expression of such, and his speech is peppered by grand gestures and overly-verbose vocabulary. 
\newline
In his position as town crier he is extremely dedicated, and has never missed a day of work- if he does so it’s cause for concern! He typically fact-checks his news fairly rigorously, and will never flat-out lie. He does, however, have an unfortunate tendency to exaggerate to “hold the public’s attention”. In this manner, 10 goblins slain will become 50, and a wyrmling dragon an ancient. This tendency is well-known by the townsfolk, in fact, players will have more of a problem convincing anyone he isn’t exaggerating.    
\subsection{Marcella Ghent, Owner and Proprietor of The Cloak And Stagger Inn}
An older lady with a rather checkered past, Mistress Ghent (As she prefers to be known) has given up a life of thievery in the Imperial City for that of a tavern-owner on the frontier. With a few little items on the side, naturally. She is typically genial and easy-going with her patrons, occasionally bantering with the somewhat suspicious Tal’ax. 
\newline
Marcella does, in fact, offer a number of useful services besides ale and a bed. She has an excellent fencing racket selling off trinkets found across the marches, and is perfectly happy to assist if players find themself in the Cloak with a troublesome… body. For a fee, of course. 
\newline
She is also apprised of potential valuable finds across the marches, and might be willing to whisper them across the bar in thieves cant if she thinks a player might be interested.  

\subsection{Tal'Ax, Captain of the Guard}
A genial watchman, formerly of the Imperial City, Tal’ax’s unique style of policing has earned him the love of the non-criminal proportion of the townsfolk. Friendly and courteous, he will often be found walking drunks home, chatting with market vendors or sitting in the Cloak and Stagger off-duty
\newline
His style of interrogation is somewhat unusual, as well. He will generally, when talking to a suspect, take out a small black notebook and begin recording everything they say, whilst questioning them about various matters relating to the offence. This will include everything, including requests to stop writing, which may be repeated back at the suspect as he writes. 
\newline
As a devoted follower of Iuris, the god of law, Tal’ax will never take bribes and will likely immediately arrest any who attempt to buy him.
\subsection{Minor NPC's}
\subsubsection{Bill Smith, The Blacksmith}
Bill Smith is is an orphan Tiefling who was adopted by blacksmiths. While often dissatisfied by his job he is an excellent blacksmith who's wares can sometimes be brought in the West Market
\subsubsection{Karten Hersteller, The Cartographer}
Karten Hersteller is a Firbolg who is rather large for his race. He is a cartographer who attempts to creates maps for Westfast, however he is often scared by the smallest of creatures so is often unsuccessful in his task.
\subsubsection{Enwen Evensong}
Enwen Evensong is a silver haired Elvin Bard who is often seen performing in The Cloak and Stagger Inn.
\section{Locations Within Westfast}
Although Westfast is a small town it contains a variety of locations.
\subsection{The Cloak and Stagger Inn}
The Cloak and Stagger Inn is the main and online inn within Westfast. It contains both a bar and lodgings. Most of the adventurers in Westfast live in this Inn. The building is mainly made of wood and is only dimly lit by torches and candles.
\subsection{Helmends Office}
Helemnds office is a large stone building. Inside the walls are lined with shelving units and various mechanical apparatuses. It is incredibly well lit in both day and night by various magical lamps.
\subsection{The West Market}
The West Market is a plot of land where merchants can set up shop to sell various goods and wares ranging from mundane expedition supplies such as rations and tents all the way to arcane objects with mystic abilities. There are no permanent shops in The West Market and merchants rotate out frequently.
\subsection{The Plaza}
The Plaza is a relatively large plot of land in the centre of Westfast. It contains the Town Hall Board (despite a lack of an actual town hall). Often events are held in The Plaza.
\subsection{The Barracks}
The Barracks is the base for the town guard, Headed by Tal'Ax. It contains lodging for the town guard and a prison.

